### 2022-09-14 dissertation/chapters/01-introduction.tex
📝 (chapter 1): Review

\Ac{ML} is one of the most popular fields of research in \ac{AI} studies today.
In recent years, \ac{ML} research has seen some notable achievements in the
academia \cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014,
      ref:quoc:2017}, as well as the industry at large \cite{ref:silver:2016,
      ref:silver:2017, ref:zoph:2017, ref:lewis:2017}.  \ac{ML} research has grown
tremendously over the past decade with successes like AlphaGo, which set new
standards for \ac{AI} capabilities by beating the world's best Go player, Lee
Sedol, 4-1 \cite{ref:san-hun:2016}.  Furthermore, an improvement on AlphaGo,
called AlphaZero, learned to play Go, \textit{tabula rasa} \footnote{Latin word
      meaning to learn from no prior knowledge.} and managed to beat AlphaGo, 100-1
\cite{ref:silver:2017}.

Over the past few years, modern hardware capabilities have improved to the
point where workloads in the field of \ac{ML} that were previously computationally
infeasible, are now possible. One such sub-field of \ac{ML} is \acp{ANN}. \acp{ANN} can generally be described as well-organised structures of mathematical computation and are inspired by the biological brain \cite{ref:engelbrecht:2007}. \acp{ANN} are the digital equivalent of how we currently understand the brain to work. \acp{ANN} can be trained, which is the equivalent of ``learnin'' from data. Learning gives rise to the ability to apply some form of decision making. This ability provides a wide-range of applications from healthcare to finance and yields great interest in the field. With the improvement of hardware came an influx of \ac{ML} researchers that focused
their attention on the training of \acp{ANN}.

A popular field of focus for studying \acp{ANN} is the process by which
these models are trained. \acp{FFNN} are specific types of
\acp{ANN} \cite{ref:reed:1999}. The most common way of training \acp{FFNN} is
\index{supervised training}supervised learning. Training of \acp{ANN} is seen as an optimisation problem. The \ac{ANN} maintains a set of parameters, referred to as ``weights'' and ``biases''. A search algorithm known as a \index{heuristic}\textit{heuristic}
\cite{ref:pearl:1984} is used to assign optimal values to the parameters of the \ac{ANN}, such that a specified objective function is minimised.

This dissertation focuses on the development of a specific type of heuristic, called a \acl{HH} to train \acp{FFNN} in a supervised learning approach. In particular, this chapter provides the reader with a brief overview of the problem domain and outlines the research problem, objectives and purpose.

The remainder of the chapter is presented as follows:

\begin{itemize}
      \item \textbf{Section \ref{sec:introduction:summary_problem_domain}} provides the reader with brief summary of the problem domain.

@@

      \item \textbf{Section \ref{sec:introduction:objectives}} presents the reader with research objectives.
      \item
      \item \textbf{Section \ref{sec:introduction:contributions}} outlines the contributions of this research to the field.

@@

\section{Summary of Problem Domain}
\label{sec:introduction:summary_problem_domain}

Historically, \ac{ML} models were built with a specific purpose in mind and
revolved around specialised applications. A notable development was that of Deep
Blue by IBM \cite{ref:keene:1996}, which managed to play chess at a grand master
level. Deep Blue was able to finish 2-4 against the greatest chess player at the
time, Gary Kasparov. Although Deep Blue lost the tournament, this was a major
breakthrough in the field of \ac{AI}. However, Deep Blue was only able to play
chess and could not be utilised for any other purposes \cite{ref:kelley:2010}.
Today, DeepMind's \ac{RL} algorithm is capable of playing all of the original
Atari games \cite{ref:mnih:2013}, but is still very limited to a small set of
problems that it can solve.

@@

This dynamic nature of the learning process leads towards the
idea that \ac{ML} models could yield better generalisation capabilities if the
learning process and learning mechanism applied are not statically defined, but
rather dynamic and under the control of some mechanism. Furthermore, a learning technique that has at its disposal a more diverse set
of learning behaviours from which it can dynamically select (when the need arises) could yield better generalisation capabilities \cite{ref:huang:2009}.

@@

\section{Problem Statement}
\label{sec:introduction:problem}

@@

\section{Motivation}
\label{sec:introduction:motivation}

@@

\section{Objectives}
\label{sec:introduction:objectives}

@@

\section{Contributions}
\label{sec:introduction:contributions}

@@

\begin{itemize}
      \item
            A novel heuristic selection operator is used that focuses on using Bayesian
            statistics to calculate the probability that a heuristic should be selected
            in order to efficiently train \acp{FFNN}. The resulting \ac{HH} is referred
            to as the \Acl{BHH}.

@@

\section{Dissertation Outline}
\label{sec:introduction:outline}

@@

>>>>

\Ac{ML} is one of the most popular fields of research in \ac{AI} studies today. In recent years, \ac{ML} research has seen some notable achievements in academia \cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014, ref:quoc:2017}, as well as the industry at large \cite{ref:silver:2016, ref:silver:2017, ref:zoph:2017, ref:lewis:2017}.  \ac{ML} research has grown tremendously over the past decade with successes like AlphaGo, which set new standards for \ac{AI} capabilities by beating the world's best Go player, Lee Sedol, 4-1 \cite{ref:san-hun:2016}.  Furthermore, an improvement on AlphaGo, called AlphaZero, learned to play Go, \textit{tabula rasa} \footnote{Latin word meaning to learn from no prior knowledge.} and managed to beat AlphaGo, 100-1 \cite{ref:silver:2017}.

Over the past few years, modern hardware capabilities have improved to the point where workloads in the field of \ac{ML} that were previously computationally infeasible, are now possible. One such sub-field of \ac{ML} is \acp{ANN}. \acp{ANN} can generally be described as well-organised structures of mathematical computation and are inspired by the biological brain \cite{ref:engelbrecht:2007}. \acp{ANN} are the digital equivalent of how we currently understand the brain to work. \acp{ANN} can be trained, which is the equivalent of ``learning'' from data. Learning gives rise to the ability to apply some form of decision making. This ability provides a wide-range of applications from healthcare to finance and yields great interest in the field. With the improvement of hardware came an influx of \ac{ML} researchers that focused their attention on the training of \acp{ANN}.

A popular field of focus for studying \acp{ANN} is the process by which these models are trained. \Acfp{FFNN} are specific types of \acp{ANN} \cite{ref:reed:1999}. The most common way of training \acp{FFNN} is \index{supervised learning}\textit{supervised learning}, which is a training technique that involves exposing the \acp{ANN} with input and comparing the produced output to that of predefined target data. Training of \acp{ANN} is seen as an optimisation problem. The \ac{ANN} maintains a set of parameters, referred to as ``weights'' and ``biases''. A search algorithm known as a \index{heuristic}\textit{heuristic} \cite{ref:pearl:1984} is used to assign optimal values to the parameters of the \ac{ANN}, such that a specified objective function is minimised.

This dissertation focuses on the development of a specific type of heuristic, called a \acl{HH} to train \acp{FFNN} in a supervised learning approach. In particular, this chapter provides the reader with a brief overview of the problem domain and outlines the research problem, objectives and purpose. The remainder of the chapter is presented as follows:

\begin{itemize}
      \item \textbf{Section \ref{sec:introduction:summary_research_domain}} provides the reader with brief summary of the problem domain. This section also provides a review of the history that lead to related \ac{ANN} research.

@@

      \item \textbf{Section \ref{sec:introduction:objectives}} presents the reader with research objectives and outlines the goals of this dissertation.

      \item \textbf{Section \ref{sec:introduction:contributions}} outlines the contributions of this research to the field.

@@

The reader is presented with the summary of the research domain next.

\section{Summary of Research Domain}\label{sec:introduction:summary_research_domain}

In order to grasp all the concepts that are included in this disseration, it is important to briefly review the landscape of the research fields that are involved, and led to the research work in this disseration. This section provides the reader with a brief summary of the research field and outlines key concepts  that contribute to the topics addressed and discussed in this disseration.

Historically, \ac{ML} models were built with a specific purpose in mind and revolved around specialised applications. A notable development was that of Deep Blue by IBM \cite{ref:keene:1996}, which managed to play chess at a grand master level. Deep Blue was able to finish 2-4 against the greatest chess player at the time, Gary Kasparov. Although Deep Blue lost the tournament, this was a major breakthrough in the field of \ac{AI}. However, Deep Blue was only able to play chess and could not be utilised for any other purposes \cite{ref:kelley:2010}. Today, DeepMind's \ac{RL} algorithm is capable of playing all of the original Atari games \cite{ref:mnih:2013}, but is still very limited to a small set of problems that it can solve. Although the computational requirements were lagging behind, these achievements where impressive at the time.

@@

The dynamic nature of the learning process leads towards the idea that \ac{ML} models could yield better generalisation capabilities if the learning process and learning mechanism applied are not statically defined, but rather dynamic and under the control of some mechanism. Furthermore, a learning technique that has at its disposal a more diverse set of learning behaviours from which it can dynamically select (when the need arises) could yield better generalisation capabilities \cite{ref:huang:2009}.

@@

\section{Problem Statement}\label{sec:introduction:problem}

@@

The following section provides the authors motivation for this research and outlines the value that this research brings to the field.

\section{Motivation}\label{sec:introduction:motivation}

Section \ref{sec:introduction:problem} provides the reader with the research problem being addressed in this disseration. This section provides compelling arguments for why this research is important and valuable to the field.

@@

\section{Objectives}\label{sec:introduction:objectives}

@@

The following section outlines the research contributions that this disseration hope to bring to the field.

\section{Contributions}\label{sec:introduction:contributions}

@@

\begin{itemize}
      \item A novel heuristic selection operator is used that focuses on usi ng Bayesianstatistics to calculate the probability that a heuristic should be selectedin order to efficiently train \acp{FFNN}. The resulting \ac{HH} is referredto as the \Acl{BHH}.

@@

\section{Dissertation Outline}\label{sec:introduction:outline}

@@

The following chapter provides the reader with the background information required on \acp{ANN}.
